---
title: "GHC Demo Assignment"
subtitle: "CSC 110 – Fall 2025"
author: "Duc Nguyen"
date: "10/23/2025"
format:
  html:
    toc: true
    toc-depth: 2
    toc-location: left
    theme:
      light: sandstone
      dark: darkly
  pdf: default
---

```{r setup}
#| output: false
library(tidyverse)
```

## Homework

```{r}
#| fig-cap: "Fuel mileage scatterplot"
ggplot(mpg, aes(x = displ, y = hwy)) +
geom_point(color = "blue") +
labs(
title = "Engine Displacement vs Highway Mileage",
x = "Engine size (L)",
y = "Highway MPG"
)
```

[Davidson College](https://www.davidson.edu)

* Other classes that I am taking
  + ECO 202
  + ECO 211
  + COM 101

1. Queen of Tears
2. Crash Landing On You
3. We Bare Bears

Here is a footnote reference,[^1] and another.[^longnote]

[^1]: Here is the footnote.

[^longnote]: Here's one with multiple blocks.

    Subsequent paragraphs are indented to show that they
belong to the previous footnote.

        { some.code }

    The whole paragraph can be indented, or just the first
    line.  In this way, multi-paragraph footnotes work like
    multi-paragraph list items.



$$
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
$$
```{mermaid}
flowchart LR
  A[Hard edge] --> B(Round edge)
  B --> C{Decision}
  C --> D[Result one]
  C --> E[Result two]
```

> Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal.

::: callout-note
This is a callout note.
::: 

::: callout-tip
This is a callout tip.
:::

::: {.callout-important collapse="true"}
This is a callout important.
:::

{{< pagebreak >}}

## Reflection

One technique I found especially useful was adding a **table of contents** in Quarto. It makes long webpages much easier to navigate and gives the reader a clear overview of each section. I can see myself using this feature in the final project so viewers can jump directly to specific parts of my analysis instead of scrolling endlessly. Using a TOC also helps me think about the *hierarchy* of my sections and how to structure my arguments clearly.

Another tip I enjoyed experimenting with was customizing the **theme**. Being able to switch between `light` and `dark` modes adds personality to the webpage and improves readability for different users. I learned how simple it is to change the appearance by editing the YAML header and adding a few lines of code. For my final project, I plan to choose a clean theme that matches the tone of my topic and ensures visual consistency across all pages.

Finally, I liked working with **callout blocks**, especially the collapsible one. Callouts help emphasize key points or warnings without cluttering the main text. I can imagine using a `callout-important` section in my final project to highlight limitations or data caveats, and maybe a `callout-tip` for notes on how others could reproduce my analysis. This feature makes the webpage feel more interactive and professional.

